\textsf{\textbf{Droplet Electro-Bouncing in Low-Gravity}}

### 2017-11-08 doc/figures/asgsr_scratch.tex
changes to figures

\newpage
\subsection*{Parameter Estimation}
We find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = D$, using a direct search method (\emph{Nelder-Mead}). 
\begin{equation*}
\mbox{min} \hspace{2 mm} \chi^2 = \sum^n_{i=1} \frac{\left({yD(\mathbf{x})}_i - yG(\mathbf{x})_i \right)^2}{yG(\mathbf{x})_i}
\end{equation*}
\[\mbox{where} \hspace{2 mm} yG(\mathbf{x}) \hspace{2 mm} \mbox{is a solution of} \hspace{2 mm} m y'' = \frac{1}{2} \rho C_D A_d^2 {y'}^2 + q \mathbf{E}(y) + \frac{1}{2} \left| E(y) \right|^2 \nabla \epsilon\]
\begin{eqnarray*} \mbox{} \hspace{2 mm} \begin{split} \mathbf{x} = \left\{ \begin{array}{ll}      & q\\
		  &	V_d\\
          & \sigma 
          \end{array} \right. 
          \end{split} \hspace{2 mm} \mbox{subject to} \hspace{2 mm} \begin{split}
          g = \left\{ \begin{array}{ll}
          & V_d \pm u_{exp}\\
      	  & \sigma \pm u_{exp}\\
      	  & y_0 \pm u_{exp}\\
      	  & t_0 \pm u_{exp}\\
          \end{array} \right. 
          \end{split}
\end{eqnarray*}
\end{document}

>>>>

\newpage
\subsection*{Parameter Estimation}
We find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = D$, using a direct search method (\emph{Nelder-Mead}). 
\begin{equation*}
\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^n_{i=1} \frac{\left({yD(\mathbf{x})}_i - yG(\mathbf{x})_i \right)^2}{yG(\mathbf{x})_i}
\end{equation*}
\[\mbox{where} \hspace{2 mm} yG(\mathbf{x}) \hspace{2 mm} \mbox{is a solution of} \hspace{2 mm} m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + \frac{1}{4} \frac{K q^2}{y^2} + \frac{1}{2} {E(y)}^2 \nabla \epsilon\]
\begin{eqnarray*} \mbox{} \hspace{2 mm} \begin{split} \mathbf{x} = \left\{ \begin{array}{ll}      & q\\
		  &	V_d\\
          & \sigma 
          \end{array} \right. 
          \end{split} \hspace{2 mm} \mbox{subject to} \hspace{2 mm} \begin{split}
          g = \left\{ \begin{array}{ll}
           V_d &\pm \hspace{2 mm} u_{exp}\\
      	   \sigma &\pm  \hspace{2 mm} u_{exp}\\
      	   y_0 &\pm \hspace{2 mm} u_{exp}\\
      	   t_0 &\pm \hspace{2 mm} u_{exp}\\
          \end{array} \right. 
          \end{split}
\end{eqnarray*}
\end{document}

### 2017-11-08 doc/manuscript/outline.tex
changes to figures

\begin{abstract}
\noindent
Notes on electric fields `n stuff.
\end{abstract}

@@

\begin{itemize}
\item In the absence of gravity the influence of usually negligible electrostatic forces can suprise the unready. We have observed electrostatic accelerations 0.5 $mL$ water droplets on the order of 10's of $cm/s^2$ in proximity to charged surfaces. It's quite easy to (accidentally) charge dielectric surfaces as well. Simply washing fluorinated surfaces with water can induce large surface potentials (hundreds of volts).

@@

\item We can extrapolate a simple rule if thumb in droplet ``escape velocity'' of impacts and time scales for returns.

>>>>

\begin{abstract}
\noindent
It's an abstract.
\end{abstract}

\section{Introduction}

@@

\begin{itemize}
\item In the absence of gravity the influence of usually negligible electrostatic forces can surprise the unready. We have observed electrostatic accelerations 0.5 $mL$ water droplets on the order of 10's of $cm/s^2$ in proximity to charged surfaces. It's quite easy to (accidentally) charge dielectric surfaces as well. Simply washing fluorinated surfaces with water can induce large surface potentials (hundreds of volts).

@@

\item By scale arguments and perturbation of solutions to the equations of motion we find several simple rules of thumb in droplet ``escape velocity'' of impacts, length scales and time scales for returns.
